Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-02-27 automatica/paper.tex
added contributions over CAV'17

@@

\note{Add note explaining relationship of this work with previously published papers. }

>>>>

This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17} 
in the following directions:
\begin{itemize}
\item While \cite{DBLP:conf/cav/AbateBCCDKKP17} is restricted to systems
  modeled in discrete time, in the current paper we present a model for
  soundly evaluating reachability in a combined continuous-discrete time/space.
\item A further limitation of the work in \cite{DBLP:conf/cav/AbateBCCDKKP17}
  is its restriction to fixed-point arithmetic, meaning that fixed-point numbers
  were employed for the representation of both the plant and the controller, as well as for
  the operations performed by each of them.
  Conversely, in the current paper we also make use of floating-point arithmetic
  and compare the two approaches. Additionally, we enhance the implementation with an SMT backend, allowing us to also use reals in order to represent the states of the plant.
\end{itemize}

@@

%\note{Add note explaining relationship of this work with previously published papers. }
